---
title: "r2dii.match 0.0.2 is now on CRAN"
description: |
  It's compatible with R back to 3.4 and dplyr 0.8.5; but update ASAP!
author:
  - name: Mauro Lepore
    url: https://github.com/maurolepore
base_url: https://2degreesinvesting.github.io/ds-at-2dii/
date: 2020-06-05
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: true
categories:
  - r2dii
  - software development
  - release
preview: preview.jpg
twitter:
  site: "@mauro_lepore"
  creator: "@mauro_lepore"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r Post-title}
```

r2dii.match 0.0.2 is now on CRAN. r2dii.match provides tools to match financial portfolios with climate data. This release is compatible with R back to v3.4 and with dplyr v0.8.5, but you should update as soon as possible.

```{r Installation-instructions}
```

You can install it from CRAN with:

```r
install.packages("r2dii.match")
```

```{r Usage-instructions}
```

Then use it with:

```{r}
library(r2dii.match)
```

```{r NEWS-details}
```

[All changes in this version are internal](https://github.com/2DegreesInvesting/r2dii.match/releases/tag/v0.0.2). In general, internal changes do not affect you as a user in the short term; but in the long term, they might. In this post I will explain a few details of our internal work; the goal is to help you decide whether or not you should update R or R packages.

## Do our packages work on your computer?

[We ensure the R-pacakges we build work with these computer environments](https://github.com/2DegreesInvesting/r2dii.match/blob/master/cran-comments.md):

* Operative systems: Work on Windows, Mac, and Linux.

* Versions of R:
  * "release" (latest-release, now R-4.0); 
  * "devel" (in-development next-release); 
  * "oldrel" (last-release, now R-3.6); 
  * and two older minor releases (now R-3.5 and R-3.4).

* R packages: Latest version on CRAN.

## When will our packages no longer support older versions of R or R packages (e.g. dplyr 0.8.5)?

If your computer does not meet the requirements we test for, our packages might not work. We enforce that your version of R is -- at least -- the oldest one we test for. But we rarely enforce specific versions of R packages. Although our packages might not work with your outdated packages, it is up to you to decide when to update them.

## [Should I update all my R packages frequently? Yes/No? why?](https://community.rstudio.com/t/should-i-update-all-my-r-packages-frequently-yes-no-why/5856)

> You will always eventually have a reason that you must update. So you can either do that very infrequently, suffer with old versions in the middle, and experience great pain at update. Or admit that maintaining your system is a normal ongoing activity, and do it more often.

> There are definitely situations where people have good reason to not update or to do so infrequently or at specific milestones. But I personally encounter many more who suffer from the opposite: updating too infrequently, without any specific reason or because they fear disruption (which makes it worse in the end).

-- Jenny Bryan

In general, you should update your R packages as often as it is possible and convenient; maybe weekly. Popular packages change rapidly. For example, we now support dplyr v0.8.5 but you should update to dplyr v1.0.0 ASAP. [Some features of v0.8.5 have been superseded in v1.0.0](
https://dplyr.tidyverse.org/news/index.html#superseded). In order to adhere to best practices we may enforce v1.0.0 any time.

```{r Acknowledgements, echo=FALSE}
# bash
# git shortlog --summary tag-oldrel..tag-release
# For example: Who contributed to r2dii.match 0.0.2 (since 0.0.1)?
# git shortlog --summary 0.0.1..0.0.2

thank <- function(x) {
  x <- sort(x)
  paste0("[", x, "]", sprintf("(https://github.com/%s)", x), collapse = ", ")
}
contributors <- c(
  "jdhoffa",
  "maurolepore"
)
```

## Acknowledgements

While this release includes commits from only a few of us (`r thank(contributors)`), it is thanks to ideas and feedback from many more colleagues at 2DII.